---
title: "analysis"
author: "Scott Brenstuhl"
date: "June 4, 2016"
output: html_document
---

```{r requirments, echo = FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(rgdal)
library(ggplot2)
library(ggmap)
library(maptools)

```

### Getting the data

https://data.sfgov.org/Culture-and-Recreation/Recreation-Park-Department-Park-Info-Dataset/z76i-7s65

http://sfparkscores.weebly.com/feature-scores.html

https://public.tableau.com/vizql/w/ParkScoresv4/v/Features/viewData/sessions/1D8A178C40944FBC93011B5CB095BE4E-0:0/views/4120671465633930416_17547768605657168597?maxrows=200

```{r, echo=FALSE}
sqlite <- dbDriver("SQLite")
con <- dbConnect(sqlite, "parks_discovery/db.sqlite3")
parks <- dbGetQuery(con,
                    "SELECT * 
                    FROM parks_discovery_park")

park_attribs <- dbGetQuery(con,
                    "SELECT * 
                    FROM parks_discovery_parkattribute")

zip2hood<- read.csv("data/zipcode_to_neighborhood.csv", stringsAsFactors = FALSE)

park_attribs <- park_attribs[!(park_attribs$attribute %in% parks$neighborhood),]
park_attribs <- park_attribs[!(park_attribs$attribute %in% parks$size),]
park_attribs <- park_attribs[!(park_attribs$attribute %in% parks$park_type),]

attrib_grid <- table(park_attribs$park_id, park_attribs$attribute)
attrib_grid <- data.frame(id = rownames(attrib_grid),
                          as.data.frame.matrix(attrib_grid))

park_data <- merge(parks, attrib_grid,  by= "id", all = TRUE) 
park_data[is.na(park_data)] <- 0

park_data <- merge(zip2hood, park_data, on = "neighborhood")
View(park_data)
```


```{r}
atribs <- names(attrib_grid) %>% 
    .[.!="id"]

total_atributes <- colSums(park_data[names(park_data) %in% atribs])
sort(total_atributes/nrow(park_data))

```

Hardscapes are thins like sidewalks, gazibos, non-athletic court concreate slabs (Tank hill)

```{r, echo = FALSE}
by_neighborhood <- group_by(park_data, neighborhood, zipcode) %>%
    summarize(count = n(), 
              tot_acreage = sum(acreage),
              dog_areas = sum(Dog.Play.Areas)/count,
              child_areas = sum(Children.s.Play.Areas)/count,
              courts = sum(Outdoor.Courts)/count,
              athletic_fields = sum(Athletic.Fields)/count,
              garden = sum(Community.Garden)/count,
              mini_parks = sum(Mini.Park)/count,
              seating = sum(Table.Seating.Areas)/count) %>%
    arrange(desc(count))

```

```{r, echo=FALSE}
map<-get_map(location='san francisco', zoom=12, maptype='roadmap')
ggmap(map)
ggmap(map)+
    geom_point(aes(x=longitude, y=latitude),
                      data=park_data)

# Guide I used 
#http://www.markhneedham.com/blog/2014/11/17/r-ggmap-overlay-shapefile-with-filled-polygon-of-regions/

sfn <- readOGR("data/sfzipcodes","SFZipCodes") %>%
    spTransform(CRS("+proj=longlat +datum=WGS84"))
ggplot(data = sfn, aes(x = long, y = lat, group = group)) + 
    geom_path()

# names(sfn)
sfn.f <- sfn %>% fortify(region = 'zip')

# I need to learn more about this line
SFNeighbourhoods <- merge(sfn.f, sfn@data, by = 'id')

# possibly should do a full merge so none get dropped
sf <- merge(SFNeighbourhoods, by_neighborhood, 
            by.x = 'id', by.y= 'zipcode') %>%
    arrange(order)


ggplot(sf, aes(long, lat, group = group)) + 
    geom_polygon(aes(fill = athletic_fields))


ggmap(map) + 
    geom_polygon(aes(fill = athletic_fields, x = long, y = lat, group = group), 
                 data = sf,
                 alpha = 0.8, 
                 color = "black",
                 size = 0.2)
```


### Todo:
Acres of park per mile in each neighborhood (need to map back to zip, file 
needed is in data dir)

Decide how to deal with Golden gate park more eligantly 

why no review of these parks (or did I drop them at some point)?
UPDATE: I think I fixed this but should confirm
parks$name[!(parks$name %in% park_data$name)]

Can I pull in elevation data to guess which parks have the best views?



